### 2020-01-27 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
исправил ссылки

It should also be noted that during the calculation process, it may be necessary to change the selected values of the feasible concessions $\delta_i$, $1 \leq i < s$; the concessions may be quite rigid or, conversely, excessively large. In general, one may need to change the order of importance in efficiency criteria. Such assumptions necessitate a more general formulation of how to solve the MCOlex problem and to provide possible solutions to many problems of the form (\ref{eq:8})
\begin{equation}\label{eq:8}
\mathbb{P}_t=\{ P_1,P_2,\dots,P_t\},
\end{equation}
which can be changed dynamically during calculations by adding new or deleting existing multicriteria optimization problems. In general, such an approach defines a new class of optimization problems: multistage lexicographic multicriteria optimization problems (MMCOlex).

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:7}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of constraints values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ), 0\leq \theta_j\leq 1,1\leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,1\leq i\leq k \}}.
	\end{matrix}
\end{equation}

>>>>

It should also be noted that during the calculation process, it may be necessary to change the selected values of the feasible concessions $\delta_i$, $1 \leq i < s$; the concessions may be quite rigid or, conversely, excessively large. In general, one may need to change the order of importance in efficiency criteria. Such assumptions necessitate a more general formulation of how to solve the MCOlex problem and to provide possible solutions to many problems of the form (\ref{eq:7})
\begin{equation}\label{eq:8}
\mathbb{P}_t=\{ P_1,P_2,\dots,P_t\},
\end{equation}
which can be changed dynamically during calculations by adding new or deleting existing multicriteria optimization problems. In general, such an approach defines a new class of optimization problems: multistage lexicographic multicriteria optimization problems (MMCOlex).

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:20}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of constraints values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ), 0\leq \theta_j\leq 1,1\leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,1\leq i\leq k \}}.
	\end{matrix}
\end{equation}
